Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-28 manuscript.Rmd
Remove other event counts

For both the target-only (n = `r num_target`) and the target and source data (n = `r num_source_target`) described above, time
series of the count of all events were generated by summing the total number of
events on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events for each
day that had an intensity rating greater than zero. Lastly, time series of count
of negative events were generated by summing the number of ICEWS events for each
day that had an intensity rating less than zero.

>>>>

For both the target-only and the target and source data described above, time
series of the count of all events were generated by summing the total number of
events on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events for each
day that had an intensity rating greater than zero. Lastly, time series of count
of negative events were generated by summing the number of ICEWS events for each
day that had an intensity rating less than zero.
